---
title: "Challenge Week #4"
author: "Krishna Agrawal"
format:
  html:
    self-contained: true
    code-tools: true
    code-fold: true
execute:
  echo: true
  error: true
---

# Set-Up

```{r setup}
#| message: false
library(tidyverse)
library(here)


```

# Data

```{r}
#|message: false
#|warning: FALSE
# This code is copied from the lab
avocados <- read.csv(here("Week#4", "Lab 4", "avocado.csv"))
avocados <- avocados |>
  mutate( region =  as.factor(region)) |>
  rename(SmallAvocados = X4046,
         LargeAvocados = X4225,
         XLargeAvocados = X4770)


major_region_df <- data.frame(major_region = c('GreatLakes', 
                                               'SouthCentral', 
                                               'Southeast', 
                                               'West', 
                                               'Midsouth', 
                                               'Northeast', 
                                               'Plains', 
                                               'NorthernNewEngland'))


state_df <- data.frame(state = c("California", 
                                 "SouthCarolina"))

city_avocados <- avocados |>
  anti_join(y = major_region_df, by = c('region' = 'major_region')) |>
  anti_join(y = state_df, by = c('region' = 'state')) |>
  filter(region != "TotalUS")


region_avocado <- avocados |>
  inner_join(major_region_df, by = c('region' = 'major_region'))

cali_avocados <- data.frame(cali_region = c('LosAngeles', 
                                            'SanDiego', 
                                            'Sacramento', 
                                            'SanFrancisco'))


# Created Dataset to get the mean price of avocados for each region and year combination
california_avocados <- city_avocados |>
  inner_join(cali_avocados, by = c('region' = 'cali_region')) |>
  mutate( region =  as.factor(region)) |>
  group_by(region, year) |>
  summarise(avg_price = mean(AveragePrice))

```

## Viewing Data

```{r}
#| message: false
#| output: false
# We have years from 2015 to 2018 and need median housing pricing from 2015 to 2018
"
LA 
  2015 - 502750	
  2016 - 522520
  2017 - 577690
  2018 - 588140
  
San Diego
  2015 - 530000
  2016 - 568000
  2017 - 605000
  2018 - 618500

"
#https://www.laalmanac.com/economy/ec37.php
  
"
San Fransisco 
  2015 - 729690
  2016 - 775820
  2017 - 882000
  2018 - 905000
"
#https://www.car.org/marketdata/data/housingdata
"
Sacramento 
  2015 -247575
  2016 - 286167
  2017 - 314776
  2018 - 332451
"
#https://www.zillow.com/home-values/20288/sacramento-ca/

# Create vectors with median housing pricing

la_data <- c(502750, 522520, 577690, 588140)
sd_data <- c(530000, 568000, 605000, 618500)
sf_data <- c(729690, 775820, 882000, 905000)
sac_data <- c(247575, 286167, 314776, 332451)
year <- c(2015, 2016, 2017, 2018)

# Create data set with median housing prices
med_housing_price <- data.frame(Year = year,
                                LosAngeles = la_data,
                                SanDiego = sd_data,
                                SanFrancisco = sf_data,
                                Sacramento = sac_data)

med_housing_price <- med_housing_price |>
  pivot_longer(cols = c('LosAngeles',"SanDiego", "SanFrancisco", "Sacramento"),
              names_to = "city",
              values_to = 'price')
```

```{r}
# Joining the two datasets by year and region

california_avocados <- california_avocados |>
  left_join(y = med_housing_price, by = c('region' = 'city', 'year' = "Year")) |>
  mutate(year = as.character(year),
         year = as.factor(year))




```

```{}
```

```{r}

ggplot(data = california_avocados) +
  geom_point( mapping = aes(x = price, y = avg_price, color = year)) +
  facet_wrap(~region) +
  labs(y = "Avg Avocado Price", x = "Median House Price")

```

From the visualizations above it seems as if there is no true relationship between the median price of homes and the average price of Hass Avocados. There is no linear or exponential relationship between housing prices and avocado prices. For example, throughout every region, we had an increase in home prices in 2018 but a drastic decrease in avocado prices. These two prices could be tied together as avocado prices could increase with the cost of living. We also have limited data in this analysis but from this we can say that buying avocado is probably not keeping you from buying a home.
