---
title: "Lab 2"
author: "Krishna Agrawal"
format:
  html:
    self-contained: true
    code-tools: true
    code-fold: true
execute:
  echo: true
  error: true
---

# Set-up

```{r setup}
library(tidyverse)
library(here)
```

# Data Context

| Column          | Description                        |
|-----------------|------------------------------------|
| record_id       | Unique id for the observation      |
| month           | month of observation               |
| day             | day of observation                 |
| year            | year of observation                |
| plot_id         | ID of a particular plot            |
| species_id      | 2-letter code                      |
| sex             | sex of animal ("M", "F")           |
| hindfoot_length | length of the hindfoot in mm       |
| weight          | weight of the animal in grams      |
| genus           | genus of animal                    |
| species         | species of animal                  |
| taxon           | e.g. Rodent, Reptile, Bird, Rabbit |
| plot_type       | type of plot                       |

# Reading the Data into R

### **Question 1**

```{r data}
# Code for question 1! 
surveys <- read_csv(here("Week#2", "Lab_Week_2", "surveys.csv"))
```

## Inspecting the Data

```{r inspect-data}
# Code for questions 2 & 3!
dim(surveys)
str(surveys)
```

### **Question 2**

What are the dimensions of these data?

15 columns and 30,463 rows

### **Question 3**

What are the data types of the variables in the dataset?

     $ record_id      : num 
     $ month          : num 
     $ day            : num 
     $ year           : num 
     $ plot_id        : num 
     $ species_id     : chr 
     $ sex            : chr 
     $ hindfoot_length: num 
     $ weight         : num 
     $ date           : Date
     $ day_of_week    : chr 
     $ plot_type      : chr 
     $ genus          : chr 
     $ species        : chr 
     $ taxa           : chr 

## Scatterplot

### **Question 4**

```{r scatterplot}
# Code for question 4! 
ggplot(data = surveys, mapping = aes(x = weight , y = hindfoot_length)) +  
   geom_point()

```

### **Question 5**

```{r alpha}
#Code for question 5!
ggplot(data = surveys, mapping = aes(x = weight, y = hindfoot_length)) +  
   geom_point(alpha=.3)
```

### **Question 6**

```{r jitter}
# Code for question 6! 
ggplot(data = surveys, mapping = aes(x = weight, y = hindfoot_length)) +  
   geom_jitter(alpha=.3)
```

## Faceting

### **Question 7**

```{r facet}
# Code for question 7
ggplot(data = surveys, mapping = aes(x = weight, y = hindfoot_length)) +  
   geom_jitter(alpha=.3) +
   facet_wrap(~ species)
```

# Boxplots & Density Ridges

### **Question 8, 9, 10, 11, 12**

```{r boxplot-jitter-points}
# Code for question 8 (and 9 and 10 and 11 and 12)! :) 
#8
ggplot(data = surveys, mapping = aes(x = species, y = weight)) +  
   geom_boxplot() 
#9
ggplot(data = surveys, mapping = aes(x = species, y = weight)) +  
   geom_boxplot() +
   geom_point() 
#10
ggplot(data = surveys, mapping = aes(x = species, y = weight)) +  
   geom_boxplot() +
   geom_jitter() 
#11
ggplot(data = surveys, mapping = aes(x = species, y = weight)) +  
   geom_boxplot() +
   geom_jitter(color = "darkseagreen")
#12
ggplot(data = surveys, mapping = aes(x = species, y = weight)) +  
   geom_boxplot(outlier.shape = NA) +
   geom_jitter(color = "darkseagreen")
```

# Customization

### **Question 13**

```{r}
# Code for question 13! 
ggplot(data = surveys, mapping = aes(x = species, y = weight)) +
   geom_boxplot(outlier.shape = NA) +
   geom_jitter(color = "darkseagreen") +
   labs(x = "Species of Animal",
        y = "Weight (grams)", 
        title = "Weight in grams vs Species of Animal")
```

### **Question 14**

```{r}
# Code for question 14!
ggplot(data = surveys, mapping = aes(y = species, x = weight)) +
   geom_boxplot(outlier.shape = NA) +
   geom_jitter(color = "darkseagreen") +
   labs(y = "Species of Animal",
        x = "Weight (grams)", 
        title = "Species of Animal vs Weight in grams")
```
